A formal approach but practical approach in train regulation

### 2025-06-24 paper/main.tex
garde I

%% Guard
\definecolor{guardcolor}{rgb}{0.53, 0.66, 0.42}
\newcommand{\guardFmt}[1]{{\color{guardcolor} \ensuremath{\mathtt{#1}}}}
\newcommand{\guardT}{\guardFmt{T}}
\newcommand{\guardS}{\guardFmt{S}}
\newcommand{\guardR}{\guardFmt{R}}
\newcommand{\guardG}{\guardFmt{G}}

%% Buffer
\newcommand{\bufferFmt}[1]{#1}
\newcommand{\head}[1]{\ensuremath{{\tt hd}(#1)}}
\newcommand{\buflen}[1]{\ensuremath{{\tt len}(\bufferFmt{#1})}}
\newcommand{\bufhead}[1]{\head{\bufferFmt{#1}}}
\newcommand{\buftail}[1]{\ensuremath{{\tt tl}(\bufferFmt{#1})}}
\newcommand{\emptyList}{\ensuremath{\varepsilon}}
\newcommand{\bufTrainSet}{\ensuremath{\bufferFmt{\mathbb{B}_t}}\xspace}
\newcommand{\bufSigSet}{\ensuremath{\bufferFmt{\mathbb{B}_s}}\xspace}
\newcommand{\bufTrain}{\ensuremath{\bufferFmt{B_t}}\xspace}
\newcommand{\bufSig}{\ensuremath{\bufferFmt{B_s}}\xspace}

@@

To each safe step $X = (\vec{x}_i)_{i \in \trains}$, we can associate a system state $C(X) = \redTuple{\guardG}{\bufferFmt{B}}{\stateTuple{\trainSeq}{\regulator}{\switches}{\signals}} $ as follows. 
\begin{itemize}
\item $\guardG = \guardT$,
\item $\bufferFmt{B} = \emptyList$,
\item for each train $\tid{id}$, $\trainSeq[id] = \trainTuple{\tid{id}}{\bid{id}}{d}{\su{d}{x^{id}_{k_{id}}}}$ with $\langle d,\sigma\rangle = \text{priv}(\vec{x}^{id})$,
\item $R = \langle E, 0, \emptyset\rangle$, $E$ being defined below,
\item $\sigma$ is the unique network configuration shared by all privileged pairs (here we suppose that there is at least one(!) train),
\item $F = \blocks \times \directions \to \{\sigred, \siggreen \}$:
$$
(\bid{id}, d) \mapsto \left \{ \begin{array}{ll}
\sigred & \text{if } \exists \tid{id} \in \trains \text{ such that }  \bid{id} = x^{id}_{k_{id}} \text{ and } \langle d,\sigma\rangle = \text{priv}(\vec{x}^{id}) \\
\siggreen & \text{otherwise}
\end{array} \right.$$
\end{itemize}

@@

\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		%\includegraphics[width=\textwidth]{img/spec_pc.png}
		\caption{Spec de l'ordinateur}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		%\includegraphics[width=\textwidth+0.5cm]{img/testElem.png}
		\caption{Vérification des chemins élémentaires}
	\end{subfigure}
	\caption{Tests sur les chemins élémentaires}
\end{figure}
\label{fig:elem-tests}

>>>>

%% Guard
\definecolor{guardcolor}{rgb}{0.53, 0.66, 0.42}
\newcommand{\guardFmt}[1]{{\color{guardcolor} \ensuremath{\mathtt{#1}}}}
\newcommand{\guardT}{\guardFmt{T}}
\newcommand{\guardS}{\guardFmt{S}}
\newcommand{\guardR}{\guardFmt{R}}
\newcommand{\guardG}{\guardFmt{G}}
\newcommand{\guardI}{\guardFmt{I}}
%% Buffer
\newcommand{\bufferFmt}[1]{#1}
\newcommand{\head}[1]{\ensuremath{{\tt hd}(#1)}}
\newcommand{\buflen}[1]{\ensuremath{{\tt len}(\bufferFmt{#1})}}
\newcommand{\bufhead}[1]{\head{\bufferFmt{#1}}}
\newcommand{\buftail}[1]{\ensuremath{{\tt tl}(\bufferFmt{#1})}}
\newcommand{\emptyList}{\ensuremath{\varepsilon}}
\newcommand{\bufTrainSet}{\ensuremath{\bufferFmt{\mathbb{B}_t}}\xspace}
\newcommand{\bufSigSet}{\ensuremath{\bufferFmt{\mathbb{B}_s}}\xspace}
\newcommand{\bufTrain}{\ensuremath{\bufferFmt{B_t}}\xspace}
\newcommand{\bufSig}{\ensuremath{\bufferFmt{B_s}}\xspace}

@@

To each safe step $X = (\vec{x}_i)_{i \in \trains}$, we can associate a system state $C(X) = \redTuple{\guardI}{ \emptyList}{ \emptyList}{\stateTuple{\trainSeq{}}{\regulator}{\switches}{\signals}}$ with $\stateTuple{\trainSeq{}}{\regulator}{\switches}{\signals}$ defined as follows: 
\begin{itemize}
\item for each train $\tid{id}$, $\trainSeq[id] = \trainTuple{\tid{id}}{\bid{id}}{d}{\su{d}{x^{id}_{k_{id}}}}$ with $\langle d,\sigma\rangle = \text{priv}(\vec{x}^{id})$,
\item $R = \langle E, 0, \emptyset\rangle$, $E$ being defined below,
\item $\sigma$ is the unique network configuration shared by all privileged pairs (here we suppose that there is at least one(!) train),
\item $F = \blocks \times \directions \to \{\sigred, \siggreen \}$:
$$
(\bid{id}, d) \mapsto \left \{ \begin{array}{ll}
\sigred & \text{if } \exists \tid{id} \in \trains \text{ such that }  \bid{id} = x^{id}_{k_{id}} \text{ and } \langle d,\sigma\rangle = \text{priv}(\vec{x}^{id}) \\
\siggreen & \text{otherwise}
\end{array} \right.$$
\end{itemize}

@@

%\begin{figure}
%	\begin{subfigure}{0.5\textwidth}
%		\centering
%		%\includegraphics[width=\textwidth]{img/spec_pc.png}
%		\caption{Spec de l'ordinateur}
%	\end{subfigure}
%	\begin{subfigure}{0.5\textwidth}
%		\centering
%		%\includegraphics[width=\textwidth+0.5cm]{img/testElem.png}
%		\caption{Vérification des chemins élémentaires}
%	\end{subfigure}
%	\caption{Tests sur les chemins élémentaires}
%\end{figure}
%\label{fig:elem-tests}
